---
title: "Reproducible Research Peer Assignment 1"
author: "Erik van der Merwe"
date: "Sunday, April 19, 2015"
output: html_document
---
# Reproducible Research - Peer Assignment 1

The following document was compiled for the completion of Peer Assignment 1 in the Reproducible Reseach module for the completion of the Data Science course provided by the John Hopkins University or Coursera

## Loading and Preprocessing the Data

The following steps were taken to load the Fitbit data to R.

```{r Getting the Data}
  temp <- tempfile()
  download.file("http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip", temp)
  activity_data <- read.csv(unz(temp, "activity.csv"))
  unlink(temp)
```

Further data manipulation were done as indicated below

```{r Data Manipulation}

```

## Calculating the Mean Number of Daily Steps Taken

The amount of steps recorded on a daily basis can be seen in the bar plot derived as below.

```{r Daily Step Histogran}
  plotdata <- tapply(activity_data$steps, activity_data$date, FUN = sum, rm.na = TRUE)
  barplot(plotdata, xlab = "Date", ylab = "No. of Steps", main = "Total Steps Recorder by the FitBit device per Day")
```

The mean and median values were calculated as follow:

```{r Daily Step Mean and Median}
  step_mean <- round(mean(plotdata, na.rm = TRUE), 2)
  step_median <- median(plotdata, na.rm = TRUE)
```
Mean = `r as.character(step_mean)`
Median = `r as.character(step_median)`